---
title: "compthinking1"
subtitle: "Assessment"
date: 2023-10-15
format: html
---

Questions:
Abstraction is a key computational thinking skill: filtering out all but the key details and matching your task to the right patterns. When it comes to data, abstraction means learning how to represent complex real-world data in standard data structures. In today’s lesson you learned about the fundamental data structure in R: vectors.

Answer the following questions in your Quarto document. Choose the questions according to the lesson you completed. Pretend this assessment is a report about your research you’re sharing with a collaborator: add descriptive text and use Markdown formatting to make it easy to read.



< Team Porifera >

____________________________________________________________________
Q1

Match the following types of real-world data to their equivalent R type and explain your reasoning.

Real world data: scientific names, the count of plants in a quadrat, whether or not it rained on a sequence of days, and the reaction times of birds to disturbances in seconds

R types: logical, integer, numeric, and character



A1

scientific names: character, use letters not numbers

the count of plants in a quadrat: integer can be counted using whole number

whether or not it rained on a sequence of days: logical, can be answered in TRUE or FALSE

the reaction times of birds to disturbances in seconds: numeric, measured in decimal values, not discrete



____________________________________________________________________
Q2

Use this code chunk to answer the following questions.
```{r}
bird_mass_g <- c(100.1, 99.2, 99.3, NA, 100.0, 101.5, 94.7, 99.2, 108.2)
mean_mass <- mean(bird_mass_g)
sd_mass <- sd(bird_mass_g)
is_outlier <- bird_mass_g > mean_mass + 3 * sd_mass
num_outliers <- sum(is_outlier)
```

In plain english, what does this code chunk do?

Two of the lines have mistakes that keep the code from doing what it’s supposed to. What are the mistakes and how would you fix them?

What are the types of bird_mass_g, is_outlier, and num_outliers?



A2

line 1: make a list of numbers

line 2: calculate the mean of the numbers in the list

line 3: calculate the standard deviation of the numbers in the list

line 4: set a condition to pick out the outliers

line 5: adding the outliers...? maybe trying to count?

mistake 1: have NA in the list of numbers, have to set a condition to filter it out before calculating the mean

mistake 2: is_outlier is logical, so can not use sum



____________________________________________________________________
Q3

How could you change the first line of code in the following chunk so that median_count comes out to 5L?

```{r}
quad_counts <- c(2L, 19L, 4L, 5L, 5L, 12L, 0L, 7L)
valid_quads <- c(1, 2, 3, 5, 7)
quad_counts2 <- quad_counts[valid_quads]
median_count <- median(quad_counts2)
```



A3
```{r}
quad_counts <- c("5L", "5L", "12L", "0L", "7L", "2L", "19L", "4L")
```
I don't fully understand the question, but I changed all the integer into character, and rearranged the order to be extracted by valid_quads

